### 2021-04-22 paper/ase21/overview.tex
Reflected comments

\subsection{Specification Extraction}\label{sec:overview-spec-extract}
$\tool$ extracts the JavaScript syntax and semantics using $\jiset$,
and it extracts specification types from ECMAScript.

\paragraph{Syntax and Semantics}
ECMAScript uses a variant of extended BNF notations to describe the JavaScript syntax.
While $\jiset$ synthesizes AST structures and JavaScript parsers from
the lexical and syntactic productions in ECMAScript, $\tool$ uses only
AST structures to define their types and access corresponding syntax-directed algorithms.
ECMAScript uses abstract algorithms written in a structured natural language to
describe the JavaScript semantics. While $\jiset$ compiles abstract algorithms to functions in $\ires$,
we modify $\ires$ to make it more suitable for type analysis as
formally defined in Section~\ref{sec:ires}.

\paragraph{Types}
In addition to JavaScript types,
$\tool$ represents three kinds of specification types.
First, because ASTs are values in abstract algorithms, 
they can be stored in variables and passed as function arguments.
For ASTs, we use their production names as their
types and automatically link their corresponding syntax-directed algorithms as their fields.
Second, ECMAScript supports various record types and fields
whose possible values are defined in their corresponding tables.
For example, ``Table 9: Completion Record Fields'' in the latest
ECMAScript describes the fields of the completion records.
% The newest version contains tens of tables for record types, and they are backward compatible in general.
Thus, we manually model the fields of record types based on the tables
in the latest version and use them in a type analysis.
Third, for list-like structures, we define the empty list type
$\clist{}$ and parametric list types $\clist{\tau}$.

@@

\paragraph{Analysis Initializer} It defines the initial abstract state and the
initial set of views for a worklist. ECMAScript provides three
kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and
\textit{built-in}. Since syntax-directed algorithms and built-in algorithms have
their parameter types, we use them as entry points of type analysis.  For each entry point, the
initializer defines its abstract environment with parameter types and adds the
flow- and type-sensitive views of the entry point to the worklist.

@@

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, the \textbf{IteratorBindingInitialization}
algorithm in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
another specification bug existed in \textbf{IteratorBindingInitialization} of
\textit{FormalParameter} in Figure~\ref{fig:example}(c).  The additional \textit{environment} parameter may
contain \jscode{undefined} or an environment record exactly the same as
\textit{originalEnv} as described in the assertion on line 5.
However, the assertion missed that the initial commit
of the open development process on September 22, 2015 introduced
\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.
The assertion checker can detect such assertion failures.

\paragraph{Operand Checker} After the function call initialization, the
parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} in Figure~\ref{fig:example}(d) is invoked
with the argument \jscode{true}.  The \jscode{Math.round} built-in library first
converts the given parameter \textit{x} to its corresponding number value
\textit{n} using \textbf{ToNumber}, and then performs the remaining
steps using \textit{n}.  However, a contributor mistakenly used
\textit{x} instead of \textit{n} on lines 3 and 4 on September 11, 2020.
This bug caused the algorithm to compare the boolean value \jscode{true} with the
numeric value 0.5 or 0 in the example JavaScript program.
This bug lived for two days until another contributor fixed it, and
the operand checker can detect such bugs.

>>>>

\subsection{Specification Extraction}\label{sec:overview-spec-extract}
$\tool$ extracts the JavaScript syntax and semantics using $\jiset$
and extracts specification types from ECMAScript.

\paragraph{Syntax and Semantics}
ECMAScript describes the JavaScript syntax in an EBNF notation
and the semantics using abstract algorithms written in a structured natural language.
From ECMAScript, $\jiset$ synthesizes AST structures for syntax and 
compiles the abstract algorithms to $\ires$ functions with parameters
and local variables for semantics.  For example, the algorithm step
``\raisebox{-0.55ex}{\includegraphics[width=0.55\columnwidth]{img/compile-example}}''
is compiled to an $\ires$ instruction $\kwlet \; \code{baseObj}\; \code{=}
\escaped\!  \code{ToObject(V.Base)}$.  To make it suitable for type analysis,
we modify $\ires$ as formally defined in Section~\ref{sec:ires}.

\paragraph{Types}
In addition to JavaScript types,
$\tool$ represents three kinds of specification types.
First, because ASTs are values in abstract algorithms, 
they can be stored in variables and passed as function arguments.
For ASTs, we use their production names as their
types and automatically link their corresponding syntax-directed algorithms to their fields.
Second, ECMAScript supports various record types and fields
whose possible values are defined in their corresponding tables.
For example, ``Table 9: Completion Record Fields'' in the latest
ECMAScript describes the fields of the completion records.
% The newest version contains tens of tables for record types, and they are backward compatible in general.
Thus, we manually model the fields of record types based on the tables
in the latest version and use them in a type analysis.
Third, for list-like structures, we define the empty list type
$\clist{}$ and parametric list types $\clist{\tau}$.

@@

\paragraph{Analysis Initializer} It defines the initial abstract state and the
initial set of views for a worklist. ECMAScript provides three
kinds of abstract algorithms: \textit{normal}, \textit{syntax-directed}, and \textit{built-in}. 
As for entry points of type analysis, we use syntax-directed algorithms and built-in algorithms
because they have their parameter types.  For each entry point, the
initializer defines its abstract environment with parameter types and adds the
flow- and type-sensitive views of the entry point to the worklist.

@@

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, \textbf{IteratorBindingInitialization}
in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
another bug existed in \textbf{IteratorBindingInitialization} of
\textit{FormalParameter} in Figure~\ref{fig:example}(c).
The additional \textit{environment} parameter may
contain \jscode{undefined} or an environment record exactly the same as
\textit{originalEnv} as described in the assertion on line 5.
\inred{However, the assertion missed that the initial commit
of the open development process on September 22, 2015 introduced
\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.}
The assertion checker can detect such assertion failures.

\paragraph{Operand Checker} After the function call initialization, the
parameter \jscode{x} has the value \jscode{true}, and \jscode{Math.round} in Figure~\ref{fig:example}(d) is invoked
with the argument \jscode{true}.  The \jscode{Math.round} built-in library first
converts the given parameter \textit{x} to its corresponding number value
\textit{n} using \textbf{ToNumber}, and performs the remaining
steps using \textit{n}.  However, a contributor mistakenly used
\textit{x} instead of \textit{n} on lines 3 and 4 on September 11, 2020.
This bug caused the algorithm to compare the boolean value \jscode{true} with the
numeric value 0.5 or 0 in the example code.
This bug lived for two days until another contributor fixed it, and
the operand checker can detect them.
